\cvsection{Projects}
\begin{cvsimpleprojects}

  \cvsimpleproject
    {Events Schedule}
    {
    % \textbf{}
      \begin{cvitems}
        \item {Designed and developed an events schedule which allows user to register/login and  add/update/remove events.}
        \item {Built the web page with \textbf{React} by refactoring an open source template.}
        \item {Created a \textbf{MongoDB} database to store user info with event data, and built \textbf{RESTful} APIs with \textbf{Node.js}, \textbf{Express.js} and \textbf{Mongoose}.}
        \item {Implemented server-side token based user authentication with \textbf{Passport.js}, \textbf{JWT} and \textbf{Bcrypt}.}
        \item {Utilized \textbf{Joi} to validate request and \textbf{Winston} to log requests as well as corresponding response content and response time.}
      \end{cvitems}
    }
    
    % \cvsimpleproject
    % {Satellite image classification}
    % {
    % % \textbf{}
    %   \begin{cvitems}
    %     \item {Built a deep convolutional neural network based on U-Net architecture using Keras with TensorFlow backend.}
    %     \item {Fed in 500MB satellite images data and trained the network to classify each pixel into one of six landscape classes.}
    %     \item {Optimized the number of down-samplings to avoid overfitting, classification accuracies of all landscape classes are increased to 90.11\% - 98.30\% after training. }
    %   \end{cvitems}
    % }
    
    \cvsimpleproject
    {News App for Android}
    {
    % \textbf{}
      \begin{cvitems}
        \item {Built a Tinder-like News app based on \textbf{MVP} architectural pattern.}
        \item {Created \textbf{ViewPager} with \textbf{BottomBar} that holds News/Save/Setting Tabs’ state in the MainActivity concurrently.}
        \item {Utilized Mindorks’s \textbf{PlaceHolderView} to implement swiping gestures for liking/disliking the news.}
        \item{Integrated \textbf{Retrofit} and \textbf{Rxjava} to pull the latest news data from NewsAPI.org.}
      \end{cvitems}
    }
    
  \cvsimpleproject
    {Location based Social Network}
    {
    % \textbf{}
      \begin{cvitems}
        \item {Created a geo-based social network web application with \textbf{React} and \textbf{Ant Design}.}
        \item {Utilized \textbf{GeoLocation API} and \textbf{Google Map API} to implement features such as "Create Post", "Nearby Posts As Gallery" and "Nearby Posts In Map".}
        \item {Built a basic token based registration/login/logout flow with \textbf{React Router v4} and server-side user authentication with \textbf{JWT}.}
      \end{cvitems}
    }
    
    
    
    \cvsimpleproject
    {E-commerce Website}
    {
    % \textbf{}
      \begin{cvitems}
        \item {Designed and built an online shopping website for users to browse products, edit shopping cart and checkout.}
        \item {Implemented the web application using \textbf{Spring Web MVC} to achieve loosely coupling. }
        \item {Created a \textbf{MySQL} database and used \textbf{Hibernate} to perform database operations.}
        \item {Developed a \textbf{Spring Web Flow} for checkout and enabled \textbf{Spring Security} to implement user authentication as well as authorization.}
        \item {Built an advertising platform that implements second-price bidding algorithm, and integrate the platform into E-commerce website to deliver best ads to users.}
      \end{cvitems}
    }
    
    
    
    % \cvsimpleproject
    % {NBA Player Strength Visualization}
    % {
    % % \textbf{}
    %   \begin{cvitems}
    %     \item {Developed a dashboard using React, D3 and Ant Design backed by API from stats.nba.com to visualize individual player’s shot data, including a shot chart and user profile view.}
    %     \item {Created 4 extra filters and 2 shot themes(hexbin and scatter) to provide more customized visualization on the shot chart.}
    %     \item {Built an autocomplete player search bar providing a list of players(image and name) in the suggestion list.}
    %   \end{cvitems}
    % }
    
    \cvsimpleproject
    {Nearby Event Search and Recommendation}
    {
    % \textbf{}
      \begin{cvitems}
        \item {Designed and developed a website to show nearby events pulled from Ticketmaster API and recommend events based on user’s favorite events.}
        \item {Built an interactive web page with \textbf{HTML}, \textbf{CSS}, vanilla JavaScript and \textbf{AJAX} technique.}
        \item {Implemented \textbf{RESTful} APIs using Java servlets and created a \textbf{MySQL} database to store user and event data.}
        \item {Designed a content-based recommendation algorithm to handle event recommendation.}
        \item {Deployed server side to \textbf{Amazon EC2} to handle 150 queries per second tested by \textbf{Apache JMeter}.}
      \end{cvitems}
    }
    
    

    
 
\end{cvsimpleprojects}
